Expression QTL hotspot dissection with mediation analysis and pleiotropy testing

### 2019-07-29 analysis/paper/hotspot-one-chromosome.Rmd
moved code chunks to hotspots-paper.Rmd from hotspot-one-chromosome.Rmd

```{r}
if (!file.exists(here("analysis", "data", "derived_data", "expr.rds"))){
  download.file("https://datadryad.org/bitstream/handle/10255/dryad.166774/Attie_DO378_eQTL_viewer_v1.Rdata?sequence=2",
              destfile = here("analysis", "data", "raw_data", "Attie_DO378_eQTL_viewer_v1.Rdata")
              )
  load(here("analysis", "data", "raw_data", "Attie_DO378_eQTL_viewer_v1.Rdata"))
  saveRDS(dataset.islet.rnaseq$lod.peaks, here("analysis", "data", "derived_data", "lod_peaks.rds"))
  saveRDS(dataset.islet.rnaseq$annots, here("analysis", "data", "derived_data", "annots.rds"))
  saveRDS(dataset.islet.rnaseq$expr, here("analysis", "data", "derived_data", "expr.rds"))
}
```

```{r}
lod_peaks <- readRDS(here("analysis", "data", "derived_data", "lod_peaks.rds"))
annots <- readRDS(here("analysis", "data", "derived_data", "annots.rds"))
expr <- readRDS(here("analysis", "data", "derived_data", "expr.rds"))
```

@@

```{r}
local_annot2 <- local_annot %>%
  filter(middle <= hot_upper, middle >= hot_lower) %>% 
  arrange(desc(lod))
```

>>>>

@@

```{r}
local_annot2 <- local_annot %>%
  filter(middle <= hot_upper + 1, middle >= hot_lower - 1) %>% 
  arrange(desc(lod))
```

### 2019-07-29 analysis/paper/hotspots-paper.Rmd
moved code chunks to hotspots-paper.Rmd from hotspot-one-chromosome.Rmd

@@

```{r, tmem189-scatter, fig.cap="Colors correspond to mediation by Tmem189"}
bar <- foo %>%
  filter(local_symbol == "Tmem189")

p <- tibble(nonlocal_symbol = rownames(pm[indic_nonlocal, indic_nonlocal])[ord_nonlocal], index = 1:length(nonlocal_symbol)) %>%
  inner_join(bar, by = "nonlocal_symbol") %>% 
  left_join(nonlocal_annot, by = c("nonlocal_symbol" = "symbol")) %>%
  ggplot() + geom_point(aes(y = pos, x = index, color = lod_diff > 1.5, nonlocal = nonlocal_symbol, lod_diff = lod_diff))

ggplotly(p)
```

>>>>

```{r}
if (!file.exists(here("analysis", "data", "derived_data", "expr.rds"))){
  download.file("https://datadryad.org/bitstream/handle/10255/dryad.166774/Attie_DO378_eQTL_viewer_v1.Rdata?sequence=2",
              destfile = here("analysis", "data", "raw_data", "Attie_DO378_eQTL_viewer_v1.Rdata")
              )
  load(here("analysis", "data", "raw_data", "Attie_DO378_eQTL_viewer_v1.Rdata"))
  saveRDS(dataset.islet.rnaseq$lod.peaks, here("analysis", "data", "derived_data", "lod_peaks.rds"))
  saveRDS(dataset.islet.rnaseq$annots, here("analysis", "data", "derived_data", "annots.rds"))
  saveRDS(dataset.islet.rnaseq$expr, here("analysis", "data", "derived_data", "expr.rds"))
}
```

```{r}
lod_peaks <- readRDS(here("analysis", "data", "derived_data", "lod_peaks.rds"))
annots <- readRDS(here("analysis", "data", "derived_data", "annots.rds"))
expr <- readRDS(here("analysis", "data", "derived_data", "expr.rds"))
```

@@
